Open-source landscape for 3D CSEM modelling

### 2020-04-10 manuscript/Manuscript.tex
Figures for Block Model

@@

Mention \cite{GJI.13.Miensopust}, which is a similar thing, but for 3D
modelling and inversion for MT.

Simple block (one to three blocks) model similar to \cite{GJI.13.Miensopust};
potentially with a bit a funkier source (say, finite length rotated bipole and
finite length receivers). In this case I would only compare inline and
crossline responses.

\begin{itemize}
  \item VTI resistivity
  \item \simpeg => use OcTree for this example? That would be awesome!
  \item Show Ex, Ey, Ez, Hx, Hy, Hz
\end{itemize}

Tables:

%
\tabl[btp]{comp1}{Caption.}{
  \centering
\begin{tabular}{lccrS[table-format=2.4]rl}
  \toprule
  %
  Code & Method & Mesh & \#Cells & {CPU} & RAM & Computer \\
  \midrule
  %
  \custem & FE  & FE & & & & \\
  \emg3d  & FIT & FD & & & & \\
  \petgem & FE  & FE & & & & \\
  \simpeg & FD  & OcTree & & & & \\
  %
  \bottomrule
\end{tabular}}%
%

%
\plot*{block-model}{width=.6\textwidth}{
   Block model, consisting of a layered background, in which three blocks are
   embedded.
}
%

%
\plot*{layered-result}{width=.6\textwidth}{
   Comparison of the layered model.
}
%

%
\plot*{block-result}{width=.6\textwidth}{
   Comparison of the block model.
}
%

\subsection{Marlim R3D}

@@

All files to reproduce the shown results and more are available at
\todo{zenodo}\dots.

>>>>

In this numerical section compute the responses for two different models to
verify that these different 3D codes yield the same electromagnetic responses.
The first model is a simple one consisting of a layered, anisotropic
background, in which three blocks are embedded, and the second model is a very
complex, realistic model.

@@

\cite{GJI.13.Miensopust} published a review of two workshops dealing with the
verification of magnetotelluric forward and inversion codes, hence a similar
exercise to what we do here for CSEM codes. The block model is a derivation of
the \emph{Dublin Test Model 1}, a model from their first workshop. We took the
same layout of the blocks but adjusted the dimensions and resistivities to a
typical, marine CSEM problem, as shown in Figure~\ref{fig:block-model}. We
additionally added a layered background with vertical transverse isotropy
(VTI).

\imycom[DW]{Next:\\
  - Describe models in text\\
  - Write text for layered and block model\\
  - Start tables for them\\
  - Move to Marlim\\
  - Discussion\\
  - Conclusions\\
  - Send to Raphael
}

%
\plot*{block-model}{width=.6\textwidth}{
  Sketch of the block model. The layered model consists of an air layer, a
  water layer, a thin top-layer and then a thick background layer, and at the
  bottom a resistive basement layer. All three blocks are embedded in the thick
  background layer, which has VTI with $\lambda=\sqrt{2}$.
}
%

% %
% \tabl[btp]{comp1}{Caption.}{
%   \centering
% \begin{tabular}{lccrS[table-format=2.4]rl}
%   \toprule
%   %
%   Code & Method & Mesh & \#Cells & {CPU} & RAM & Computer \\
%   \midrule
%   %
%   \custem & FE  & FE & & & & \\
%   \emg3d  & FIT & FD & & & & \\
%   \petgem & FE  & FE & & & & \\
%   \simpeg & FD  & OcTree & & & & \\
%   %
%   \bottomrule
% \end{tabular}}%
% %

%
\plot*{results-layered-0}{width=\textwidth}{
   Comparison of the layered model at y=0km.
}
%

%
\plot*{results-layered--3}{width=\textwidth}{
   Comparison of the layered model at y=-3km.
}
%

%
\plot*{results-block--3}{width=\textwidth}{
   Comparison of the block model at y=-3km.
}
%

%
\plot*{results-block-0}{width=\textwidth}{
   Comparison of the block model at y=0km.
}
%

%
\plot*{results-block-3}{width=\textwidth}{
   Comparison of the block model at y=+3km.
}
%

\clearpage  % TODO: Just for now while drafting, remove later!
\subsection{Marlim R3D}

@@

All files to rerun the different models with the four codes and reproduce the
shown results are available at \todo{zenodo}\dots.
